Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-18 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:18	13:57:32	(Tue18.Aug)

\subsection{Receive Beamforming}

@@

Let the receiver be an $M$ element uniform linear array. Call the the data from the $m$th channel $x_m[\theta,n]$, where the azimuth angle $\theta$ and range sample $n$ is the focus point. To simplify notation, we make the dependence on $\theta$ implicit from now on. By definition, the beamformer output $z[n]$ can be expressed as the weighted sum of all the delayed data samples:
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{z}
\end{align}
where $w_m$ is the weight factor assigned to channel $m$.

>>>>

\newpage
\subsection{Receive Beamforming}

@@

Assume that the wavefield has been sampled by an $M$ element uniform linear array, and that the signal signature has been removed by a matched filter. The data from the $m$th channel $x_m[\theta,n]$, where the azimuth angle $\theta$ and range sample $n$ is the focus point. To simplify notation, we make the dependence on $\theta$ implicit from now on. By definition, the beamformer output $z[n]$ can be expressed as the weighted sum of all the delayed data samples:
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{z}
\end{align}
where $w_m$ is the weight factor assigned to channel $m$.
